\textbf{Hardware accelerator topologies in heterogeneous systems: an evaluation in the security domain}

### 2019-12-08 reports/paper.tex
wording
wording II

\begin{figure}
  \centering
  \resizebox{0.3\textwidth}{!}{
    \begin{minipage}{0.5\textwidth}
      \centering
      \include{media/tightly_acc}
    \end{minipage}
  }
  \caption{Tightly-coupled HWACCs: accelerator is moved into CPU datapath,
    similar to Functional Units (FUs).}
\end{figure}

@@

The industry standard ciphers might impose too much of a burden on deeply
embedded, low power systems that need the ability to communicate securely over
an unsecured channel. Thus, different organizations have hosted competitions to
foster the development of lightweight ciphers, targeting both resource-limited
software and hardware implementations.

>>>>

\begin{figure}
  \centering
  \resizebox{0.3\textwidth}{!}{
    \begin{minipage}{0.5\textwidth}
      \centering
      \include{media/tightly_acc}
    \end{minipage}
  }
  \caption{Tightly-coupled HWACCs: accelerator is moved into CPU datapath,
    operating similarly to microarchitectural Functional Units (FUs).}
\end{figure}

@@

Industry standard ciphers such as AES might impose too much of a burden on deeply
embedded, low power systems that need the ability to communicate securely over
an unsecured channel. Thus, different organizations have hosted competitions to
foster the development of lightweight ciphers, targeting both resource-limited
software and hardware implementations.
